---
title: Introduction to pair programming
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, results=FALSE, cache=TRUE)
```

# What is pair programming?

```{r b2b-and-f2f}
gridExtra::grid.arrange(
  crotchet::read_graphviz("src/back-to-back.gv"),
  crotchet::read_graphviz("src/face-to-face.gv"),
  nrow = 1
)
```

# Pair programming and agile software development

```{r book-covers, out.width="50%"}
gridExtra::grid.arrange(
  crotchet::read_image("img/brooks-1974-cover.png"),
  crotchet::read_image("img/raymond-2001-cover.png"),
  nrow = 1
)
```

# The mythical man-month (Brooks, 1974)

```{r mythical-man-month}
library(tidyverse)
divide_and_conquer <- data_frame(
  x = 1:9,
  y = 1/x
)

unpartitionable <- data_frame(
  x = 1:9,
  y = 1.5
)

complex <- data_frame(
  x = 1:9,
  y = c(9, 8, 7.2, 6.8, 7.8, 9.1, 11.1, 13, 16)
)

examples <- bind_rows(
    divide_and_conquer,
    unpartitionable,
    complex,
    .id = "type"
  ) %>%
  group_by(type) %>%
  mutate(
    y_norm = ifelse(type == "2", y, (y - mean(y))/sd(y)),
    type_label = factor(type, levels = c("1", "2", "3"), labels = c("Divide and Conquer", "One at a Time", "Complex"))
  )

ggplot(examples) +
  aes(x, y_norm) +
  geom_smooth(method = "loess", se = FALSE, span = 1) +
  facet_wrap("type_label") +
  scale_x_continuous("Men", labels = NULL) +
  scale_y_continuous("Months", labels = NULL) +
  theme_bw(base_size = 20)
```

# Why pair?

Reasons for pair programming:

* **Student-Teacher.** To learn something you don't already know, or practice a skill you need to improve.
* **Teamwork.** To accomplish something together you could not have accomplished on your own.

# Goals for pairs

* **Student-Teacher.** Student learns from Teacher, Teacher gets better at teaching.
* **Teamwork.** Teammates play to each other's strengths and accomplish something together.
 
# What are we going to work on?

> Pairs should be working to solve some problem.

* **Practice problem.** Take a problem off the shelf together.
* **A real problem.** Work on a problem that will be used beyond the Pair Night.

# Practice problems

- Advent of Code
- Kaggle
- Example project (e.g., from a book)

# Real problems

- Find the expert!
- GitHub issues
- Make a thing you both want to exist

# Who are we going to work with?

- Put your name in the hat.
- Find a pair on your own.

# Timeline

- 10min: Introduction and House Rules
- 60min: Pair #1
- 60min: Pair #2

