---
title: Introduction to pair programming
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE)
```

# What is pair programming?

```{r engine="dot"}
digraph {
  fontname=Helvetica;
  node[shape=circle label="" style=filled];
  rankdir=LR;
  
  f_player1, b_player1  // order clusters last to first
  
  subgraph cluster0 {
    label="Back to back";
    b_player1 -> b_player1_laptop[dir=none];
    b_player2 -> b_player2_laptop[dir=none];
    
    b_player1_laptop -> b_player1_end[minlen=2];
    b_player2_laptop -> b_player2_end[minlen=2];
  }
  
  subgraph cluster1 {
    label="Face to face";
    { f_player1, f_player2 } -> f_shared_laptop[dir=none];
    f_shared_laptop -> f_shared_laptop_end[minlen=2];
  }
  
  b_player1, b_player2, f_player1, f_player2[fillcolor="#8DA0CB"];
  b_player1_laptop, b_player2_laptop, f_shared_laptop[shape=rectangle fillcolor="#66C2A5"];
  b_player1_end, b_player2_end, f_shared_laptop_end[style=invis width=0];
}
```

# Why pair?

- To learn something you don't already know, or practice a skill you need to
  improve. (Student-Teacher)
- To accomplish something together you could not have accomplished on your own.
  (Teamwork)

# Goals for pairs

Student-Teacher
:   Student adopts Teacher's knowledge.

Teamwork
:   Teammates play to each other's strengths.
 
# What are we going to work on?

> Pairs should be working to solve some problem.

Practice problem
:   Take a problem off the shelf together.

A real problem
:   Help someone with their problem/get help with your problem,
    or solve a real problem together.

# Practice problems

- Advent of Code
- Kaggle
- Example project (e.g., from a book)

# Real problems

- Find the expert!
- GitHub issues
- Make a thing you both want to exist

# Who are we going to work with?

- Put your name in the hat.
- Find a pair on your own.

# Timeline

- 10min: Introduction and House Rules
- 60min: Pair #1
- 60min: Pair #2

